Papers

### 2024-02-16 quarto/index.qmd
update

---
about:
  id: az-heading
  template: trestles
  image: img/aston.jpg
  image-width: 200px
  image-shape: rounded
  links:
    - icon: twitter
      href: https://twitter.com/astonzhangAZ
    - icon: bi-envelope
      href: img/email.png
    - icon: github
      href: https://github.com/astonzhang
    - icon: google
      href: https://scholar.google.com/citations?user=WXOaxKMAAAAJ

---

>>>>

---
about:
  id: az-heading
  template: trestles
  image: img/aston.jpg
  image-width: 200px
  image-shape: rounded
  links:
    - icon: twitter
      href: https://twitter.com/astonzhangAZ
    - icon: bi-envelope
      href: img/email.png
    - icon: github
      href: https://github.com/astonzhang
    - icon: google
      href: https://scholar.google.com/citations?user=WXOaxKMAAAAJ
    - icon: linkedin
      href: https://www.linkedin.com/in/astonzhang/
---
